### 2017-09-29 TF-vldb2018/sec-intro.tex

Given a task and a social network $G(V, E)$, where $V$ is a set of experts labeled with skills and $E$ reflects the collaboration relations among the experts,
the {\em top-$k$ team formation} problem (\teamF) is to find a list of $k$ highly collaborative teams of experts in $G$ such that each satisfies the skill requirements of the task.
Various approaches~\cite{Lappas09,Kargar11,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12} have been proposed for \teamF,
and fall into two categories in terms of the way to improve the collaborative compatibility of team members:
 (1) minimizing team communication costs,
defined with \eg the diameter, minimum spanning tree and the sum of pairwise member distances of the induced subgraph~\cite{Lappas09,Kargar11,ArisLuca12,SamikKVM12}, and
(2) maximizing team communication relations,
\eg the density of the induced subgraph~\cite{GajewarS12,realTeamForm13}.
Further, \cite{GajewarS12} and \cite{realTeamForm13} consider a practical setting that introduces a lower bound on the number of individuals with a specific skill in a team, and an upper bound of the total team members, respectively.

@@

An HR manager may help to set up a team for developing a new software product,
and she searches $G_1$ (without dashed edges) for proper candidates.
The desired team has
(1) one \kw{PM}, and one to two \kw{BAs}, \kw{UDs}, \kw{SAs}, \kw{SDs} and \kw{STs}, such that
(2) the \kw{PM} should collaborate with \kw{SAs}, \kw{BAs} and \kw{UDs} well, and the \kw{SDs} and \kw{STs} should collaborate with each other well and both with \kw{SAs} well.

@@

\revise{One can verify that none of existing methods suffice to identify the above desired teams.
They can only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13} in search condition (1),
while cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints in search condition (2) (see details in Example~\ref{exa-teamF}).}
 \end{example}

@@

\begin{figure}[tb!]
\begin{center}
\includegraphics[scale=1.15]{./fig/motivation-example.eps}
\end{center}
\vspace{-3.5ex}
\caption{Motivation example}
\label{fig-motivation-example}
\vspace{-5ex}
\end{figure}

@@

A natural question is how to further capture the {\em structural and capacity constraints} in a unified model for team formation?
We essentially introduce a revision of {\em graph pattern matching} for team formation to fill in this gap.

Given a pattern graph $P$ and a data graph $G$, graph pattern matching is to find all subgraphs in $G$ that match $P$, and has been extensively studied~\cite{Ullmann76,infsimu95,FanLMTWW10,MaCFHW14,Guanfeng15,FanCount16}.  Intuitively, patterns $P$ captures the structural constraint, and we extend graph pattern matching semantics to solve the team formation problem. As shown in Fig.~\ref{fig-motivation-example},  the desired team requirement can be expressed by the pattern graph $P_1$ (ignore dashed edges), such that the nodes represent the skill requirements, the edges specify the topology constraint, and the bounds on nodes are the capacity constraint.

@@

\vspace{1.0ex}
Finding desired teams typically needs a lot of labor efforts, and it is even common for professionals to refine search conditions multiple times in order to find ideal teams~\cite{SajjadPG12,HabibiP15}. 
Moreover, real-life graphs are often big and constantly evolve over time~\cite{FanWW13-tods}. That is, team formation is accompanied with a highly dynamic environment.
%
\revise{However, it is often too costly to recompute top-$k$ teams from scratch in response to pattern and data updates.
These highlight the need for incremental algorithms to compute the updated top-$k$ teams.
As opposed to batch algorithms, incremental algorithms avoid re-computing from scratch by re-using previous results.
Traditional incremental algorithms for graph queries including graph pattern matching queries are proposed to compute changes in response to data updates, which has a lot of work~\cite{FanLMTWW10,FanWW13-tods,FanHT17}. 
However, the study on incremental algorithms for graph pattern updates is in its vacancy.

\eat{
Given a pattern graph $P$ and a data graph $G$, the graph pattern matching results $P(G)$ in $G$ for $P$ and changes $\Delta G$ to $G$ as input, 
the traditional incremental matching problem is to compute changes $\Delta O$ to $P(G)$ such that $P(G\oplus\Delta G)$=$P(G)\oplus \Delta O$.
Here $\oplus$ denotes applying changes $\Delta S$ to $S$, when $S$ is data graph $G$ or query result $P(G)$.
It is to improve response time by reducing computations on big $G$ to small $\Delta G$ and $\Delta O$.}%%%EAT

\begin{example}
\label{exm-motivation-inc}
Recall $P_{1}$ and $G_{1}$ in Example~\ref{exm-motivation} and continue.

\sstab{(1)} When the manager gets the match result, \ie the top-$k$ teams $P_{1}(G_{1})$ to $P_{1}$ in $G_{1}$, 
she may find $P_1$ is too restrictive to find sensible matches.
Therefore, she enters a pattern update $\Delta P_1$ on $P_1$, composed of an edge 
deletion $(\kw{SD},\kw{ST})^-$.
We denote $P_{1}\oplus\Delta P_{1}$ the updated pattern.
It is much better to derive $P_{1}\oplus\Delta P_{1}(G_{1})$ from $P_{1}(G_{1})$
than a computation for $P_{1}\oplus\Delta P_{1}$ in $G_{1}$ from scratch.
%\looseness=-1

\sstab{(2)} When a data update $\Delta G_1$ comes on $G_1$, composed of an edge insertion $(\kw{SD_3},\kw{ST_3})^+$.
Similar with (1), it is better to compute $P_{1}(G_{1}\oplus\Delta G_{1})$ from $P_{1}(G_{1})$ incrementally.

\sstab{(3)} Even better, when it comes to the case pattern $\Delta P_{1}$ and data updates $\Delta G_{1}$ come together, it is desirable to compute $P_{1}\oplus\Delta P_{1}(G_{1}\oplus\Delta G_{1})$ from $P_{1}(G_{1})$ incrementally.
\end{example}

This motivates us to study the {\em dynamic top-k team formation} problem (\dynteamF), to handle continuous 
pattern and data updates, separately and simultaneously.
As a basis of \dynteamF, we also investigate the incremental problem for graph pattern matching on pattern updates. 
The definition can be formulated along the same line with existing data incremental problems.
%different with data incremental algorithms that preserve some desirable properties that the recomputation can be {\em bounded}  by the changes in the input and output as the impact of data updates can be localized~\cite{Reps96, FanLMTWW10,FanWW13-tods,FanHT17}, 
However, devising pattern incremental algorithms is quite challenging as the impact of pattern updates is global,
due to the inherent hardness of the problem.
Despite of this, we devise an effective unified incremental approach for the \dynteamF\, problem.

\warn{To our knowledge, no previous work has studied pattern updates for incremental pattern matching~\cite{FanHT17,FanWW13-tods}},
not to mention continuous and simultaneous pattern and data updates. It is the most general dynamic setting studied so far.} 
\looseness = -1

@@

\revise{
\stab (1) We propose {\em team simulation}, a revision of traditional graph pattern matching, for top-$k$ team formation problem. 
It extends existing methods by incorporating the structural and capacity constraints using pattern graphs (Section~\ref{sec-tsim}).
We formulate the dynamic top-$k$ team formation problem, to handle separate and simultaneous pattern and data updates,
in order to cope with the highly dynamic environment of team formation (Section~\ref{sec-tsim}).
\warn{To the best of our knowledge, this work gives the first investigation on pattern and simultaneous pattern and data incremental computations.} 
}

@@

>>>>

%Given a task and a social network $G(V, E)$, where $V$ is a set of experts labeled with skills and $E$ reflects the collaboration relations among the experts,
The {\em top-$k$ team formation} problem (\teamF) is to find a list of $k$ highly collaborative teams of experts such that every team satisfies the skill requirements of a certain task.
Various approaches~\cite{Lappas09,Kargar11,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12} have been proposed for \teamF,
and fall into two categories in terms of the way to improve the collaborative compatibility of team members:
 (a) minimizing team communication costs,
defined with \eg the diameter, minimum spanning tree and the sum of pairwise member distances of the induced subgraph~\cite{Lappas09,Kargar11,ArisLuca12,SamikKVM12}, and
(b) maximizing team communication relations,
\eg the density of the induced subgraph~\cite{GajewarS12,realTeamForm13}.
Further, \cite{GajewarS12} and \cite{realTeamForm13} consider a practical setting by introducing a lower bound on the number of individuals with a specific skill in a team, and an upper bound of the total team members, respectively.

@@

A headhunt helps to set up a team for developing a software product by searching proper candidates from $G_1$ (ignore dashed edges).
A desired team has
(a) one \kw{PM}, and one to two \kw{BAs}, \kw{UDs}, \kw{SAs}, \kw{SDs} and \kw{STs}, such that
(b) the \kw{PM} should collaborate with \kw{SAs}, \kw{BAs} and \kw{UDs} well, and the \kw{SDs} and \kw{STs} should collaborate with each other well and both with \kw{SAs} well.

@@

One may verify that existing methods \cite{Lappas09,Kargar11,GajewarS12,GajewarS12,realTeamForm13}, can hardly find a desired team.
They only find teams satisfying the skill requirement~\cite{Lappas09,Kargar11,GajewarS12} and the lower bound capacity requirement~\cite{GajewarS12,realTeamForm13}  (condition (a)), and cannot guarantee  the specific collaboration relationships among team members, \ie structural constraints (condition (b)).
 \end{example}

@@

\begin{figure}[tb!]
\begin{center}
\includegraphics[scale=1.15]{./fig/motivation-example.eps}
\end{center}
\vspace{-3ex}
\caption{Motivation example}
\label{fig-motivation-example}
\vspace{-4ex}
\end{figure}

@@

A natural question is how to further capture the {\em structural and capacity constraints} in a unified model for team formation?
We  introduce a revision of {\em graph pattern matching} for team formation to fill in this gap.
% 
Given a pattern graph $P$ and a data graph $G$, graph pattern matching is to find all subgraphs in $G$ that match $P$, and has been extensively studied~\cite{Ullmann76,infsimu95,FanLMTWW10,MaCFHW14,Guanfeng15,FanCount16}.  Essentially, we utilize patterns to captures the structural constraint, and revise the semantics of graph pattern matching for team formation. For instance, a desired team requirement can be specified by the pattern $P_1$ (ignore dashed edges) in Fig.~\ref{fig-motivation-example}, in which nodes represent the skill requirements,  edges specify the topology constraint, and the bounds on nodes are the capacity constraint.

@@

Another issue it that team formation is accompanied with a highly dynamic situation. It typically needs many labor efforts to find the ideal teams, and is common for professionals to refine patterns  (requirements) multiple rounds~\cite{SajjadPG12,HabibiP15}. Further, real-life graphs are often big and constantly evolve over time~\cite{FanWW13-tods}. We illustrate this with an example.

\begin{example}
\label{exm-motivation-inc}
Consider $P_{1}$ and $G_{1}$ in Example~\ref{exm-motivation} again.

\sstab{(1)} % When the manager gets the match result, \ie the top-$k$ teams $P_{1}(G_{1})$ to $P_{1}$ in $G_{1}$,
One may find that $P_1$ is too restrictive to find any sensible match in  $G_{1}$.
Hence, she needs to refine the pattern by updating $P_1$ with $\Delta P_{1}$, \eg an edge
deletion $(\kw{SD},\kw{ST})^-$.
%We denote $P_{1}\oplus\Delta P_{1}$ the updated pattern.
%It is much better to derive $P_{1}\oplus\Delta P_{1}(G_{1})$ from $P_{1}(G_{1})$
%than a computation for $P_{1}\oplus\Delta P_{1}$ in $G_{1}$ from scratch.
%\looseness=-1

\sstab{(2)} It is also common that a data update $\Delta G_1$ comes on $G_1$, \eg an edge insertion $(\kw{SD_3},\kw{ST_3})^+$.
%Similar with (1), it is better to compute $P_{1}(G_{1}\oplus\Delta G_{1})$ from $P_{1}(G_{1})$ incrementally.

\sstab{(3)} Finally, it can be the case when pattern update $\Delta P_{1}$  and data update $\Delta G_{1}$ come simultaneously on $P_1$ and $G_1$.
%,  $P_{1}\oplus\Delta P_{1}(G_{1}\oplus\Delta G_{1})$ from $P_{1}(G_{1})$ incrementally
\end{example}

This motivates us to study the {\em dynamic top-k team formation} problem, to handle continuous
pattern and data updates, separately and simultaneously. It is known that incremental algorithms avoid re-computing from scratch by re-using previous results~\cite{inc-survey}. However, incremental algorithms of graph pattern matching for pattern updates has not been investigated, though there exist incremental algorithms of graph pattern matching for dealing with data updates~\cite{FanLMTWW10,FanWW13-tods,FanHT17}.
Further, it is also challenging for incremental algorithms to handle simultaneous pattern and data updates  in a unified way.

\eat{
often too costly to recompute top-$k$ teams from scratch in response to pattern and data updates.
These highlight the need for incremental algorithms to compute the updated top-$k$ teams.
As opposed to batch algorithms, incremental algorithms avoid re-computing from scratch by re-using previous results.
Traditional incremental algorithms for graph queries including graph pattern matching queries are proposed to compute changes in response to data updates, which has a lot of work~\cite{FanLMTWW10,FanWW13-tods,FanHT17}.
However, the study on incremental algorithms for graph pattern updates is in its vacancy.

Given a pattern graph $P$ and a data graph $G$, the graph pattern matching results $P(G)$ in $G$ for $P$ and changes $\Delta G$ to $G$ as input,
the traditional incremental matching problem is to compute changes $\Delta O$ to $P(G)$ such that $P(G\oplus\Delta G)$=$P(G)\oplus \Delta O$.
Here $\oplus$ denotes applying changes $\Delta S$ to $S$, when $S$ is data graph $G$ or query result $P(G)$.
It is to improve response time by reducing computations on big $G$ to small $\Delta G$ and $\Delta O$.

As a basis of \dynteamF, we also investigate the incremental problem for graph pattern matching on pattern updates.
The definition can be formulated along the same line with existing data incremental problems.
%different with data incremental algorithms that preserve some desirable properties that the recomputation can be {\em bounded}  by the changes in the input and output as the impact of data updates can be localized~\cite{Reps96, FanLMTWW10,FanWW13-tods,FanHT17},
However, devising pattern incremental algorithms is quite challenging as the impact of pattern updates is global,
due to the inherent hardness of the problem.
Despite of this, we devise an effective unified incremental approach for the \dynteamF\, problem.

 }%%%EAT

\looseness = -1

@@

\revise{
\stab (1) We propose {\em team simulation}, a revision of traditional graph pattern matching, for top-$k$ team formation problem.
It extends existing methods by incorporating the structural and capacity constraints using pattern graphs (Section~\ref{sec-tsim}).
We formulate the dynamic top-$k$ team formation problem, to handle separate and simultaneous pattern and data updates,
in order to cope with the highly dynamic environment of team formation (Section~\ref{sec-tsim}).

}

@@

To our knowledge, this work is among the first to study simultaneous pattern and data incremental computations, no previous work has studied pattern updates for incremental pattern matching~\cite{FanHT17,FanWW13-tods}, not to mention continuous and simultaneous pattern and data updates.  This is  the most general dynamic setting for incremental computations.
